# 1. Mentoring Style {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*Does my mentoring style focus on structure or support?*

## The Mindset(s) {.unnumbered}

Authoritative mentoring blends two things at once:

- [**Support**]{style="color:#007F85;"}: warmth, care, and responsiveness toward your mentees.
  - *Survey item:* "How important is it to you, as a mentor, to build good relationships with your mentees?"
- [**Structure**]{style="color:#C0522A;"}: clear routines, expectations, and follow-through.
  - *Survey item:* "How important is it to you, as a mentor, to set clear expectations for how your team works together?"

**Polarity:** Structure ↔ Support.

This chapter looks at structure and support through **two lenses**. Your **dimensional
preference** comes from a 40-point budget, where valuing one more means valuing the other less,
so it captures which way you *lean*. Your **type** comes from your rated **skill** on
structure- and support-related mentoring competencies, which are measured independently, so you
can be high or low on each.

**Measures:**

- **Mentoring Style Values Inventory** (importance-rated; adapted from Ertesvåg, 2011). Eight
  items, four per subscale, rated 1–10 under a 40-point budget.
- **Mentoring Competency Assessment** (Fleming et al., 2013), skill-rated 1–7. Selected items
  form an independent support-skill and structure-skill composite (see *Your Type*).

## Your Dimensional Preference {.unnumbered}

Because the eight budget items share **40 points**, Support and Structure trade off against each
other: every point you add to one you take from the other, and the two always total 40. So this
score is not "how much" of each you value in absolute terms, but **which way you lean**.

Use your password to find your score(s).

```{r}
#| label: wk01-mentoring-style-compute
#| include: false
w1 <- dat |> transmute(Password = PASSWORD,
  Support   = Q6_1 + Q6_2 + Q6_3 + Q6_4,
  Structure = Q6_5 + Q6_6 + Q6_7 + Q6_8)
# leaning relative to a balanced 20/20 split of the 40 points
pref1 <- factor(dplyr::case_when(
  w1$Support - w1$Structure >  2 ~ "Support-leaning",
  w1$Support - w1$Structure < -2 ~ "Structure-leaning",
  TRUE                           ~ "Balanced"),
  levels = c("Structure-leaning", "Balanced", "Support-leaning"))
```

```{r}
#| label: wk01-mentoring-style-table
#| echo: false
score_table(w1$Password, list(Support=w1$Support, Structure=w1$Structure),
  "1. Mentoring Style: your Support and Structure point totals (out of 40)",
  extra = list(Preference = pref1))
```

## Locate Your Preference {.unnumbered}

Locate your preference relative to other peer mentors! The axis is the points you placed on
**support** (structure is 40 minus that): the far left is all structure, the far right is all
support, and **20 is a balanced split**.

```{r}
#| label: wk01-mentoring-style-plot
#| echo: false
#| fig-width: 8
#| fig-height: 4
norm_facets(list(`Structure vs Support`=w1$Support),
  xlab="Points placed on support (out of 40)", scale = c(0, 40), by = 10,
  labels = c("0\nAll structure","10","20\nBalanced","30","40\nAll support"))
```

## Your Type {.unnumbered}

Structure and support are two dimensions that result in four mentoring styles. Neither
dimension is "good" or "bad" on its own; it is the *combination* that describes how you show up
as a mentor:

| | **Low Support** | [**High Support**]{style="color:#007F85;"} |
|---|---|---|
| [**High Structure**]{style="color:#C0522A;"}| **Authoritarian:** high expectations, little warmth. Clear and demanding, but mentees may not feel safe asking for help. | [**Authoritative:**]{style="color:#005A43;"} high expectations *and* high warmth. Clear structure that mentees experience as being on their side. |
| **Low Structure** | **Uninvolved:** low on both. Mentees are largely left to themselves. | **Permissive:** warm and caring, but loose on expectations. Mentees feel supported but may drift. |

Unlike the budget above, your **type** comes from how skilled you feel at two independent sets
of mentoring competencies (from the Mentoring Competency Assessment), so all four combinations
are possible.

- [**Support skill**]{style="color:#007F85;"}: assessing mentee knowledge, estimating mentee
  ability, enhancing mentee skills, and building confidence.
- [**Structure skill**]{style="color:#C0522A;"}: setting clear relationship expectations,
  aligning expectations, and helping establish work/life balance.

```{r}
#| label: wk01-mentoring-style-type-compute
#| include: false
mca1 <- dat |> transmute(Password = PASSWORD,
  `Support skill`   = rowMeans(across(c(Assess_Under1, Assess_Under2, Assess_Under3, Foster_Indepen2))),
  `Structure skill` = rowMeans(across(c(Align_Expect1, Align_Expect2, Profess_Devel3))))
```

```{r}
#| label: wk01-mentoring-style-type-table
#| echo: false
score_table(mca1$Password,
  list(`Support skill`=mca1$`Support skill`, `Structure skill`=mca1$`Structure skill`),
  "1. Mentoring Type: your MCA support- and structure-skill composites (1–7)",
  extra = list(Type = style_type(mca1$`Support skill`, mca1$`Structure skill`)))
```

Each dot is one peer mentor. The dashed lines are the **class medians** on each skill, so
"high" and "low" mean *relative to your classmates*. Find your **Type** in the table above,
then find your quadrant.

```{r}
#| label: wk01-mentoring-style-typology
#| echo: false
#| fig-width: 7
#| fig-height: 5.4
typology_plot(mca1$`Support skill`, mca1$`Structure skill`,
  xlab = "Support skill (MCA, 1–7)", ylab = "Structure skill (MCA, 1–7)")
```

::: {.callout-note}
## Your type is a snapshot, not a fixed type
The median split means roughly a quarter of the class lands in each quadrant *by construction*.
If you sit close to a dashed line, small changes in a few answers would move you. Each quadrant
is a rough approximation of your balance between structure and support. This is not a fixed
type! You can build skill on either dimension and move from one quadrant to another over time.
:::

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## During Class
- Make note of how you provide mentees with both support and structure before, during, and after class
:::
