# 1. Mentoring Style {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

**Big Question:** *Does your style focus on structure or support?*

**Constructs:** Authoritative mentoring blends two things at once:

- [**Support**]{style="color:#007F85;"}: warmth, care, and responsiveness toward your mentees.
  - *Survey item:* "How important is it to you, as a mentor, to build good relationships with your mentees?"
- [**Structure**]{style="color:#C0522A;"}: clear routines, expectations, and follow-through.
  - *Survey item:* "How important is it to you, as a mentor, to set clear expectations for how your team works together?"

**Polarity:** Structure ↔ Support.

**Measure:** Mentoring Style Values Inventory (importance-rated; adapted from Ertesvåg, 2011).
Eight items, four per subscale, rated 1–10 for importance under a 40-point budget that
forces you to prioritize.

**Typology.** Crossing the two dimensions gives four mentoring styles. Neither dimension is
"good" or "bad" on its own; it is the *combination* that describes how you show up:

| | **Low Support** | **High Support** |
|---|---|---|
| **High Structure** | **Authoritarian:** high expectations, little warmth. Clear and demanding, but mentees may not feel safe asking for help. | **Authoritative:** high expectations *and* high warmth. Clear structure that mentees experience as being on their side. |
| **Low Structure** | **Uninvolved:** low on both. Mentees are largely left to themselves. | **Permissive:** warm and caring, but loose on expectations. Mentees feel supported but may drift. |

::: {.callout-tip}
## In Class
Watch how you balance warmth and structure when your team sets its first expectations.
:::

## Your Scores {.unnumbered}

Find your password below.

```{r}
#| label: wk01-mentoring-style-compute
#| include: false
w1 <- dat |> transmute(Password = PASSWORD,
  Support   = rowMeans(across(W1_1:W1_4)),
  Structure = rowMeans(across(W1_5:W1_8)))
```

```{r}
#| label: wk01-mentoring-style-table
#| echo: false
score_table(w1$Password, list(Support=w1$Support, Structure=w1$Structure),
  "1. Mentoring: your composite scores (1–10)",
  extra = list(Style = style_type(w1$Support, w1$Structure)))
```

## Class Distribution {.unnumbered}

```{r}
#| label: wk01-mentoring-style-plot
#| echo: false
#| fig-width: 9
#| fig-height: 3.8
norm_facets(list(Support=w1$Support, Structure=w1$Structure), xlab="Importance (1–10)", scale = c(1, 10))
```

## Your Mentoring Style {.unnumbered}

Each dot is one peer mentor. The dashed lines are the **class medians** on each dimension, so
"high" and "low" here mean *relative to your classmates*, not relative to the 1–10 scale.
Almost everyone rates both dimensions as important, so a scale-midpoint split would put the
whole class in one corner. Find your **Style** in the table above, then find your quadrant.

```{r}
#| label: wk01-mentoring-style-typology
#| echo: false
#| fig-width: 7
#| fig-height: 5.4
typology_plot(w1$Support, w1$Structure)
```

::: {.callout-note}
## Your style is a snapshot, not a label
The median split means roughly a quarter of the class lands in each quadrant *by construction*.
If you sit close to a dashed line, small changes in a few answers would move you. Read the
quadrant as a description of your current balance, not a fixed type.
:::


## Reflect

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** What is one thing you will commit to this week that reflects this mindset?
:::

