# 1. Mentoring Style {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*Does your mentoring style focus on structure or support?*

## The Mindset(s) {.unnumbered}

Authoritative mentoring blends two things at once:

- [**Support**]{style="color:#007F85;"}: warmth, care, and responsiveness toward your mentees.
  - *Survey item:* "How important is it to you, as a mentor, to build good relationships with your mentees?"
- [**Structure**]{style="color:#C0522A;"}: clear routines, expectations, and follow-through.
  - *Survey item:* "How important is it to you, as a mentor, to set clear expectations for how your team works together?"

**Polarity:** Structure ↔ Support.

**Measure:** Mentoring Style Values Inventory (importance-rated; adapted from Ertesvåg, 2011).
Eight items, four per subscale, rated 1–10 for importance under a 40-point budget that forces you to prioritize.

## Your Type {.unnumbered}

Structure and support are two dimensions that result in four mentoring styles. Neither dimension is "good" or "bad" on its own; it is the *combination* that describes how you show up as a mentor:

| | **Low Support** | [**High Support**]{style="color:#007F85;"} |
|---|---|---|
| [**High Structure**]{style="color:#C0522A;"}| **Authoritarian:** high expectations, little warmth. Clear and demanding, but mentees may not feel safe asking for help. | [**Authoritative:**]{style="color:#005A43;"} high expectations *and* high warmth. Clear structure that mentees experience as being on their side. |
| **Low Structure** | **Uninvolved:** low on both. Mentees are largely left to themselves. | **Permissive:** warm and caring, but loose on expectations. Mentees feel supported but may drift. |

## Find Your Score {.unnumbered}

Use your password to find your score(s).

```{r}
#| label: wk01-mentoring-style-compute
#| include: false
w1 <- dat |> transmute(Password = PASSWORD,
  Support   = rowMeans(across(W1_1:W1_4)),
  Structure = rowMeans(across(W1_5:W1_8)))
```

```{r}
#| label: wk01-mentoring-style-table
#| echo: false
score_table(w1$Password, list(Support=w1$Support, Structure=w1$Structure),
  "1. Mentoring: your composite scores (1–10)",
  extra = list(Style = style_type(w1$Support, w1$Structure)))
```

## Locate Your Score {.unnumbered}

Locate your score(s) relative to other peer mentors!

```{r}
#| label: wk01-mentoring-style-plot
#| echo: false
#| fig-width: 9
#| fig-height: 3.8
norm_facets(list(Support=w1$Support, Structure=w1$Structure), xlab="Importance (1–10)", scale = c(1, 10))
```

## Your Mentoring Style {.unnumbered}

Each dot is one peer mentor. The dashed lines are the **class medians** on each dimension, so
"high" and "low" here mean *relative to your classmates*, not relative to the 1–10 scale.
Almost everyone rates both dimensions as important, so a scale-midpoint split would put the
whole class in one corner. Find your **Style** in the table above, then find your quadrant.

```{r}
#| label: wk01-mentoring-style-typology
#| echo: false
#| fig-width: 7
#| fig-height: 5.4
typology_plot(w1$Support, w1$Structure)
```

::: {.callout-note}
## Your style is a snapshot, not a fixed type
The median split means roughly a quarter of the class lands in each quadrant *by construction*.
If you sit close to a dashed line, small changes in a few answers would move you. Each quadrant is a rough approximation of your balance between structure and support. This is not a fixed type! You can change your attention and behaviors to move from one quadrant to another over time.  
:::

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## During Class
- Make note of how you provide mentees with both support and structure before, during, and after class 
:::
