# 2. Motivational Style {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*Is my motivational approach to promote or prevent for my mentees' academics or social connection?*

## The Mindset(s) {.unnumbered}

Regulatory focus crosses two dimensions. The **focus** is what you are steering toward, and
the **goal** is what you are hoping to attain.

- [**Promotion**]{style="color:#5A71A8;"}: oriented toward gains, growth, and what your
  mentees could become.
  - *Survey item:* "Helping my mentees reach their full potential as researchers."
- [**Prevention**]{style="color:#453A98;"}: oriented toward safety, avoiding mistakes, and
  what could go wrong.
  - *Survey item:* "Preventing problems from derailing my mentees' research."
- **Academic referent**: your team's research project.
  - *Survey item:* "Helping my mentees make progress and grow in their research project."
- **Social referent**: belonging to the team and connections on campus.
  - *Survey item:* "Helping my mentees build a sense of belonging and connection on the team."

**Polarity:** Promotion ↔ Prevention × Academic ↔ Social.

**Measure:** Mentoring Regulatory Focus Scale, 2×2 (adapted; Higgins, 1997; Lockwood,
Jordan & Kunda, 2002). The stem is *"As a peer mentor, how much will you emphasize each?"* and
you rate twelve items, three per cell, on a 1–7 emphasis scale (1 = No emphasis, 4 = Moderate,
7 = Very strong emphasis). Focus and referent are scored separately.

## Find Your Score {.unnumbered}

Use your password to find your score(s).

```{r}
#| label: wk02-motivational-style-compute
#| include: false
w2 <- dat |> transmute(Password = PASSWORD,
  `Promotion × Academic`  = rowMeans(across(c(Pro_Acad1, Pro_Acad2, Pro_Acad3))),
  `Promotion × Social`    = rowMeans(across(c(Pro_Social1, Pro_Social2, Pro_Social3))),
  `Prevention × Academic` = rowMeans(across(c(Prev_Acad1, Prev_Acad2, Prev_Acad3))),
  `Prevention × Social`   = rowMeans(across(c(Prev_Social1, Prev_Social2, Prev_Social3))))
```

```{r}
#| label: wk02-motivational-style-table
#| echo: false
score_table(w2$Password, list(
  `Promotion × Academic`=w2$`Promotion × Academic`, `Promotion × Social`=w2$`Promotion × Social`,
  `Prevention × Academic`=w2$`Prevention × Academic`, `Prevention × Social`=w2$`Prevention × Social`),
  "2. Motivational Style: your 2×2 cell composites (1–7)",
  extra = list(
    `Promotion aim`  = goal_lean(w2$`Promotion × Academic`,  w2$`Promotion × Social`),
    `Prevention aim` = goal_lean(w2$`Prevention × Academic`, w2$`Prevention × Social`)))
```

## Locate Your Score {.unnumbered}

Locate your score(s) relative to other peer mentors!

```{r}
#| label: wk02-motivational-style-plot
#| echo: false
#| fig-width: 9
#| fig-height: 5
norm_facets(list(
  `Promotion × Academic`=w2$`Promotion × Academic`, `Promotion × Social`=w2$`Promotion × Social`,
  `Prevention × Academic`=w2$`Prevention × Academic`, `Prevention × Social`=w2$`Prevention × Social`),
  xlab="Emphasis (1–7)", scale = c(1, 7))
```

## Your Motivational Style {.unnumbered}

Each dot is one peer mentor. These two plots split your motivation into **how strongly** you
hold a focus and **what you aim it at**.

The **horizontal axis** is how strongly you hold that focus overall. The dashed line is the
**class median**, so "high" and "low" mean *relative to your classmates*, not relative to the
1–7 scale. The **vertical axis** is a difference score: how much more you aim that focus at
**academic** goals (your team's research project) than at **social** goals (belonging and
connection). Here the solid line at zero is a real anchor, not a class comparison. Above it
you lean academic, below it you lean social, and on it you weight the two equally. Find your
**Promotion aim** and **Prevention aim** in the table above.

```{r}
#| label: wk02-motivational-style-promotion
#| echo: false
#| fig-width: 7
#| fig-height: 4.6
focus_plot(w2$`Promotion × Academic`, w2$`Promotion × Social`,
           "Promotion", construct_color("Promotion", "base"), scale = c(1, 7))
```

```{r}
#| label: wk02-motivational-style-prevention
#| echo: false
#| fig-width: 7
#| fig-height: 4.6
focus_plot(w2$`Prevention × Academic`, w2$`Prevention × Social`,
           "Prevention", construct_color("Prevention", "base"), scale = c(1, 7))
```

::: {.callout-note}
## Your style is a snapshot, not a fixed type
The median split on the horizontal axis means roughly half the class sits on each side *by
construction*. If you sit close to either line, small changes in a few answers would move you.
The two plots are also independent: a strong promotion focus does not imply a weak prevention
focus, and you can aim them at different goals. Read your position as a description of your
current balance, not a fixed type.
:::

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## During Class
Make note of when your energy goes toward helping mentees gain and grow versus avoiding mistakes, and whether you aim it at their research or their sense of belonging.
:::
