# 3. Leadership Focus {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

**Big Question:** *Is your leadership style to promote or prevent for the team?*

**Constructs:** The same regulatory focus from Week 2, now applied to how you lead. Each
pole covers the same four leadership functions: goal framing, problem solving, error
management, and feedback.

- [**Promotion Leadership**]{style="color:#5A71A8;"}: frames goals around gains, builds on
  what works, encourages useful risks, and affirms what is going well.
  - *Survey item:* "I motivate my team by framing our goals around the gains and growth we can achieve."
- [**Prevention Leadership**]{style="color:#453A98;"}: frames goals around setbacks to
  avoid, fixes what is going wrong, emphasizes accuracy, and corrects errors.
  - *Survey item:* "I motivate my team by framing our goals around the problems and setbacks we need to avoid."

**Polarity:** Promotion ↔ Prevention (team leadership).

**Measure:** Promotion/Prevention Team Leadership Scale (adapted from regulatory focus
theory). Eight items rated 1–9, four per subscale.

## Your Scores {.unnumbered}

Find your password below.

```{r}
#| label: wk03-leadership-focus-compute
#| include: false
w3 <- dat |> transmute(Password = PASSWORD,
  `Promotion Leadership`  = rowMeans(across(W3_1:W3_4)),
  `Prevention Leadership` = rowMeans(across(W3_5:W3_8)))
```

```{r}
#| label: wk03-leadership-focus-table
#| echo: false
score_table(w3$Password, list(`Promotion Leadership`=w3$`Promotion Leadership`,
  `Prevention Leadership`=w3$`Prevention Leadership`),
  "3. Leadership I: your composite scores (1–9)")
```

## Class Distribution {.unnumbered}

```{r}
#| label: wk03-leadership-focus-plot
#| echo: false
#| fig-width: 9
#| fig-height: 3.8
norm_facets(list(`Promotion Leadership`=w3$`Promotion Leadership`,
  `Prevention Leadership`=w3$`Prevention Leadership`), xlab="Score (1–9)",
  scale = c(1, 9))
```

## Reflect

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** What is one thing you will commit to this week that reflects this mindset?
:::
