# 4. Feedback Orientation {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*Is your feedback preference supportive or corrective?*

## The Mindset(s) {.unnumbered}

Feedback orientation is a single **bipolar** dimension. It is not about how much feedback you
give, but about which way you lean when you give it. Neither end is better; mentees need both,
and the useful skill is knowing which one a moment calls for.

- [**Corrective**]{style="color:#985BA3;"} (the low end): feedback aimed at what needs fixing,
  the gap between the work and the standard.
  - *Survey item:* "I focus on mistakes to correct" (vs. "I focus on strengths to build on").
- [**Supportive**]{style="color:#477F2B;"} (the high end): feedback aimed at affirming and
  encouraging, building on what is already working.
  - *Survey item:* "My instinct is to affirm and encourage" (vs. "My instinct is to close the gap to the standard").

**Polarity:** Corrective ↔ Supportive.

**Measure:** Feedback Orientation, bipolar (author-created for this course). Three
semantic-differential items rated 1–7, where **1 = fully corrective** and **7 = fully
supportive**. Your score is the mean of the three items, so **4 is balanced**, below 4 leans
corrective, and above 4 leans supportive.

## Find Your Score {.unnumbered}

Use your password to find your score(s).

```{r}
#| label: wk04-feedback-orientation-compute
#| include: false
w4 <- dat |> transmute(Password = PASSWORD,
  `Feedback orientation` = rowMeans(across(W4_1:W4_3)))
# cutoffs sit between the discrete 1/3-steps a 3-item mean can take, so the
# label always matches the rounded score shown in the table.
lean4 <- factor(dplyr::case_when(
  w4$`Feedback orientation` > 4.5 ~ "Supportive-leaning",
  w4$`Feedback orientation` < 3.5 ~ "Corrective-leaning",
  TRUE                            ~ "Balanced"),
  levels = c("Corrective-leaning", "Balanced", "Supportive-leaning"))
```

```{r}
#| label: wk04-feedback-orientation-table
#| echo: false
score_table(w4$Password, list(`Feedback orientation`=w4$`Feedback orientation`),
  "4. Feedback Orientation: your bipolar score (1 = corrective … 7 = supportive)",
  extra = list(Lean = lean4))
```

## Locate Your Score {.unnumbered}

Scores for all peer mentors are visualized below. Locate your score relative to your peers.

```{r}
#| label: wk04-feedback-orientation-plot
#| echo: false
#| fig-width: 8
#| fig-height: 4
norm_facets(list(`Feedback orientation`=w4$`Feedback orientation`),
  xlab="Feedback orientation", scale = c(1, 7),
  labels = c("1\nCorrective","2","3","4\nBalanced","5","6","7\nSupportive"))
```

::: {.callout-important}
## About this measure
No validated self-report scale exists for this bipolar dimension, so these three items were
**written for this course**. They are grounded in the supportive/corrective feedback
distinction but are not a published instrument. Pilot and check reliability before reporting
results anywhere beyond this guide.
:::

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** Where do you land, and does that match how you *want* to show up for your mentees?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## During Class
Make note of whether your feedback this week leans corrective or supportive, and whether that fit the moment.
:::
