# 5. People Orientation {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*What is my view of people?*

## The Mindset(s) {.unnumbered}

An implicit theory is your working assumption about whether people can change. It matters for
mentoring because it shapes how you read a struggling mentee.

- **Growth orientation**: people's basic characteristics can substantially change.
  - *Survey item:* "Everyone, no matter who they are, can significantly change their basic characteristics."
- **Fixed orientation**: the important parts of who someone is cannot really be changed.
  - *Survey item:* "The kind of person someone is, is something very basic about them and it can't be changed very much."

**Polarity:** Fixed ↔ Growth.

**Measure:** 'Kind of Person' Implicit Theory Scale (Dweck, 1999). Eight items rated 1–6.
Fixed-mindset items are reverse-scored, so a higher composite means a stronger **growth
mindset**.

## Find Your Score {.unnumbered}

Use your password to find your score(s).

```{r}
#| label: wk05-people-orientation-compute
#| include: false
# Growth mindset: the four _R items are reverse-scored (7 - x on the 1-6 scale).
w5 <- dat |> transmute(Password = PASSWORD,
  `Growth mindset` = rowMeans(cbind(7-GrowthMind1_R, 7-GrowthMind2_R, GrowthMind3, 7-GrowthMind4_R,
                                    GrowthMind5, 7-GrowthMind6_R, GrowthMind7, GrowthMind8)))
```

```{r}
#| label: wk05-people-orientation-table
#| echo: false
score_table(w5$Password, list(`Growth mindset`=w5$`Growth mindset`),
  "5. People Orientation: your growth mindset composite (1–6)")
```

## Locate Your Score {.unnumbered}

Locate your score(s) relative to other peer mentors!

```{r}
#| label: wk05-people-orientation-plot
#| echo: false
#| fig-width: 6
#| fig-height: 3.8
norm_facets(list(`Growth mindset`=w5$`Growth mindset`), xlab="Growth mindset (1–6)",
  scale = c(1, 6))
```

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## During Class
Make note of when you assume a struggling mentee can grow versus when you write off their ability, and how that shapes your response.
:::
