# 6. Leadership Role {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*What is my leadership role?*

## The Mindset(s) {.unnumbered}

Leading a team is not one job but many. Morgeson, DeRue & Karam (2010) describe team
leadership as a set of distinct **functions** a leader can take on. This week you decide which
of ten functions you see as **your role** as a peer mentor. They fall into two groups:

- **Task leadership**: getting the work done: planning, tracking, training, and assessing.
  - *Survey item:* "As a peer mentor, it is my role to help them plan."
- **Relational leadership**: supporting the people: motivating, developing, and holding the
  team together.
  - *Survey item:* "As a peer mentor, it is my role to motivate the team to excel."

**Polarity:** Task ↔ Relational leadership.

**Measure:** Mentoring Leadership Functions inventory, adapted from Morgeson et al. (2010),
Table 2. The stem is *"As a peer mentor, it is my role to…"* and you rate each of ten
functions 1–10. You have a **budget of 50 points** to spread across the ten, so you have to
prioritize which functions are most central to your role.

- **Task functions:** help them plan · keep track of assignment due dates · train the team on
  specific research skills · provide feedback to teammates · evaluate the performance of the team
- **Relational functions:** monitor the group chat for help · motivate the team to excel ·
  encourage team members to self-manage · resolve team conflict · build friendships

## Find Your Score {.unnumbered}

Use your password to find your score(s).

```{r}
#| label: wk06-leadership-role-compute
#| include: false
w6 <- dat |> transmute(Password = PASSWORD,
  Task       = rowMeans(across(c(W6_1, W6_2, W6_4, W6_5, W6_6))),
  Relational = rowMeans(across(c(W6_3, W6_7, W6_8, W6_9, W6_10))))
lean6 <- factor(dplyr::case_when(
  w6$Task - w6$Relational >  0.5 ~ "Task-leaning",
  w6$Task - w6$Relational < -0.5 ~ "Relational-leaning",
  TRUE                           ~ "Balanced"),
  levels = c("Task-leaning", "Balanced", "Relational-leaning"))
```

```{r}
#| label: wk06-leadership-role-table
#| echo: false
score_table(w6$Password, list(Task=w6$Task, Relational=w6$Relational),
  "6. Leadership Role: your points-per-function averages (1–10)",
  extra = list(Lean = lean6))
```

## Locate Your Score {.unnumbered}

Locate your score(s) relative to other peer mentors!

```{r}
#| label: wk06-leadership-role-plot
#| echo: false
#| fig-width: 9
#| fig-height: 3.8
norm_facets(list(Task=w6$Task, Relational=w6$Relational),
  xlab="Average points per function (1–10)", scale = c(1, 10))
```

::: {.callout-important}
## About this measure
The ten functions are drawn from Morgeson, DeRue & Karam's (2010) functional model of team
leadership, but the mentoring-specific wording, the importance framing, and the 50-point
budget are **adapted for this course**. Because the points are a fixed budget, spending more
on one group of functions necessarily means spending less on the other. Re-check reliability
before reporting results beyond this guide.
:::

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## During Class
Make note of which leadership functions you actually spend your time on this week, and whether
they match the ones you said were your role.
:::
