# 6. Leadership Role {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*What is my leadership role?*

## The Mindset(s) {.unnumbered}

Leading a team is not one job but many. Morgeson, DeRue & Karam (2010) describe team
leadership as a set of distinct **functions** a leader can take on. This week you decide which
of ten functions you see as **your role** as a peer mentor. They fall into two groups:

- **Task leadership**: getting the work done: planning, tracking, and training.
  - *Survey item:* "As a peer mentor, it is my role to help them plan."
- **Relational leadership**: supporting the people: monitoring, motivating, developing, and
  holding the team together.
  - *Survey item:* "As a peer mentor, it is my role to motivate the team to excel."

**Polarity:** Task ↔ Relational leadership.

**Measure:** Mentoring Leadership Functions inventory, adapted from Morgeson et al. (2010),
Table 2. The stem is *"As a peer mentor, it is my role to…"* and you rate each of ten
functions 1–10. You have a **budget of 50 points** to spread across the ten, so you have to
prioritize which functions are most central to your role. Your **Task** and **Relational**
scores are the total points you place on each group's functions (out of 50).

- **Task functions:** help them plan · keep track of assignment due dates · train the team on
  specific research skills · provide feedback to teammates
- **Relational functions:** monitor the group chat for help · evaluate the performance of the
  team · motivate the team to excel · encourage team members to self-manage · resolve team
  conflict · build friendships

## Find Your Score {.unnumbered}

Use your password to find your score(s).

```{r}
#| label: wk06-leadership-role-compute
#| include: false
w6 <- dat |> transmute(Password = PASSWORD,
  Task       = Q11_1 + Q11_4 + Q11_6 + Q11_7,
  Relational = Q11_5 + Q11_8 + Q11_9 + Q11_10 + Q11_11 + Q11_12)
```

```{r}
#| label: wk06-leadership-role-table
#| echo: false
score_table(w6$Password, list(Task=w6$Task, Relational=w6$Relational),
  "6. Leadership Role: your point totals (out of 50)")
```

## Locate Your Score {.unnumbered}

Locate your score(s) relative to other peer mentors!

```{r}
#| label: wk06-leadership-role-plot
#| echo: false
#| fig-width: 9
#| fig-height: 3.8
norm_facets(list(Task=w6$Task, Relational=w6$Relational),
  xlab="Points (out of 50)", scale = c(0, 50), by = 10)
```

::: {.callout-important}
## About this measure
The ten functions are drawn from Morgeson, DeRue & Karam's (2010) functional model of team
leadership, but the mentoring-specific wording, the importance framing, and the 50-point
budget are **adapted for this course**. Because the points are a fixed budget, spending more
on one group of functions necessarily means spending less on the other. Task and Relational
also cover different numbers of functions (four vs six), so compare each score to the class
distribution above rather than directly to each other. Re-check reliability before reporting
results beyond this guide.
:::

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## During Class
Make note of which leadership functions you actually spend your time on this week, and whether
they match the ones you said were your role.
:::
