# 7. Leadership Target {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*Is your leadership style task or relational oriented?*

## The Mindset(s) {.unnumbered}

SPLIT is a **team-referent** measure: it asks how much the team as a whole shares leadership,
not how much you personally lead. Every item begins "As a team we…".

- [**Task leadership**]{style="color:#C0522A;"}: the team assigns work, communicates
  expectations, and tracks whether goals are met.
  - *Survey item:* "As a team we clearly assign tasks."
- [**Relational leadership**]{style="color:#007F85;"}: the team attends to concerns,
  recognizes good work, builds cohesion, and handles conflict.
  - *Survey item:* "As a team we take sufficient time to address each other's concerns."

**Polarity:** Task ↔ Relational.

**Measure:** SPLIT · task and relation subscales (Grille & Kauffeld, 2015). Ten items,
five per subscale, rated 0–100.

## Find Your Score {.unnumbered}

Use your password to find your score(s).

```{r}
#| label: wk07-leadership-target-compute
#| include: false
w7 <- dat |> transmute(Password = PASSWORD,
  `Task leadership`     = rowMeans(across(W7_1:W7_5)),
  `Relation leadership` = rowMeans(across(W7_6:W7_10)))
```

```{r}
#| label: wk07-leadership-target-table
#| echo: false
score_table(w7$Password, list(`Task leadership`=w7$`Task leadership`,
  `Relation leadership`=w7$`Relation leadership`),
  "7. Leadership Target: your composite scores (0–100)")
```

## Locate Your Score {.unnumbered}

Locate your score(s) relative to other peer mentors!

```{r}
#| label: wk07-leadership-target-plot
#| echo: false
#| fig-width: 9
#| fig-height: 3.8
norm_facets(list(`Task leadership`=w7$`Task leadership`,
  `Relation leadership`=w7$`Relation leadership`), xlab="Shared leadership (0–100)",
  scale = c(0, 100), by = 10)
```

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## During Class
Make note of whether your team leans on task coordination or on relationships to get its work done.
:::

::: {.callout-tip}
## UGPM Meeting
This is the week your printed, full mentoring profile is revealed.
:::
