# 7. Communication Style {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*What is my communication style?*

## The Mindset(s) {.unnumbered}

Nonviolent Communication describes three behaviors that keep a hard conversation connected
rather than combative.

- [**Self-connection**]{style="color:#007F85;"}: recognizing that your emotions come from
  your own thoughts and unmet needs, and staying present enough under stress to notice a
  reaction without acting on it.
  - *Survey item:* "Knowing that my emotions stem from my own thoughts and unmet needs, my emotions are not caused by others."
- [**Authentic self-expression**]{style="color:#5A71A8;"}: stating your feelings, needs, and
  requests sincerely, without accusation, and staying open to any response.
  - *Survey item:* "Being responsible for my own experience, and willing to express my feelings and needs sincerely without accusation or criticism."
- [**Empathic listening**]{style="color:#C0522A;"}: staying open and flexible, and using
  conflict to connect rather than to win.
  - *Survey item:* "Listen patiently, try to understand other people from their perspective."

**Polarity:** Violent ↔ Nonviolent.

**Measure:** Nonviolent Communication Behaviors Scale (Cheung et al., 2022). Seven items
rated 1 = Never to 4 = Frequently.

## Find Your Score {.unnumbered}

Use your password to find your score(s).

```{r}
#| label: wk07-communication-style-compute
#| include: false
comm <- dat |> transmute(Password = PASSWORD,
  `Self-connection`           = rowMeans(across(c(Selfconnect1, Selfconnect2))),
  `Authentic self-expression` = rowMeans(across(c(Selfexpress1, Selfexpress2))),
  `Empathic listening`        = rowMeans(across(c(Listen1, Listen2, Listen3))))
```

```{r}
#| label: wk07-communication-style-table
#| echo: false
score_table(comm$Password, list(`Self-connection`=comm$`Self-connection`,
  `Authentic self-expression`=comm$`Authentic self-expression`,
  `Empathic listening`=comm$`Empathic listening`),
  "7. Communication Style: your NVCBS composites (1–4)")
```

## Locate Your Score {.unnumbered}

Locate your score(s) relative to other peer mentors!

```{r}
#| label: wk07-communication-style-plot
#| echo: false
#| fig-width: 9
#| fig-height: 3.8
norm_facets(list(`Self-connection`=comm$`Self-connection`,
  `Authentic self-expression`=comm$`Authentic self-expression`,
  `Empathic listening`=comm$`Empathic listening`), xlab="Frequency",
  scale = c(1, 4), labels = c("1\nNever","2\nRarely","3\nSometimes","4\nFrequently"))
```

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## UGPM Meeting
Role play practice.
:::
