# 8. Inclusive Mentoring {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*Is my mentoring inclusive?*

## The Mindset(s) {.unnumbered}

Inclusive mentoring has two facets: what you **believe** matters, and what you actually **do**.
A mentor can value cultural awareness highly yet rarely act on it, so the two are measured
separately.

- [**Attitudes**]{style="color:#007F85;"}: how much you value being aware of race and ethnicity
  in your research mentoring.
  - *Survey item:* "It is important for mentors and mentees to discuss how race/ethnicity impacts the mentee's research experience."
- [**Behaviors**]{style="color:#C0522A;"}: how much you actually enact culturally aware
  mentoring.
  - *Survey item:* "I create opportunities for my mentees to bring up issues of race/ethnicity as they arise."

**Polarity:** Colorblind ↔ Culturally aware.

**Measure:** Cultural Diversity Awareness for Race/Ethnicity (CDA-R/E), mentor self-form,
adapted (Byars-Winston & Butz, 2021). Six items: three **Attitudes** (A2, A4, A5) and three
**Behaviors** (B1, B2, B3). This guide uses **two versions**:

- **Importance** (start of semester, pretest): *"As a mentor, how important is each of the
  following to you?"* rated 1 = Not at all important to 6 = Extremely important.
- **Current** (midpoint): *"How much do you agree with each statement about your mentoring
  right now?"* rated 1 = Strongly disagree to 6 = Strongly agree.

Comparing the two shows the gap between what you value and what you currently do. The scores
below are simulated for the **Current** version.

## Find Your Score {.unnumbered}

Use your password to find your score(s).

```{r}
#| label: wk08-inclusive-mentoring-compute
#| include: false
w8 <- dat |> transmute(Password = PASSWORD,
  Attitudes = rowMeans(across(W8_1:W8_3)),
  Behaviors = rowMeans(across(W8_4:W8_6)))
```

```{r}
#| label: wk08-inclusive-mentoring-table
#| echo: false
score_table(w8$Password, list(Attitudes=w8$Attitudes, Behaviors=w8$Behaviors),
  "8. Inclusive Mentoring: your CDA-R/E composites (1–6, Current version)")
```

## Locate Your Score {.unnumbered}

Locate your score(s) relative to other peer mentors!

```{r}
#| label: wk08-inclusive-mentoring-plot
#| echo: false
#| fig-width: 9
#| fig-height: 3.8
norm_facets(list(Attitudes=w8$Attitudes, Behaviors=w8$Behaviors),
  xlab="Agreement (1–6)", scale = c(1, 6))
```

::: {.callout-important}
## About this measure
The six items are drawn from the validated CDA-R/E scale (Byars-Winston & Butz, 2021), but the
selection of items and the **Importance** framing are **adapted for this course**. The
behavior items are also present-tensed for a mid-semester self-report (the original is
retrospective). Re-check reliability before reporting results beyond this guide.
:::

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** Where is the gap between what you value (Attitudes) and what you do (Behaviors), and what would close it?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## During Class
Make note of moments where a mentee's identity shapes their research experience, and how you respond.
:::
