# 11. Communicator {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

*What is your communication style?*

## The Mindset(s) {.unnumbered}

Nonviolent Communication describes three behaviors that keep a hard conversation connected
rather than combative.

- [**Self-connection**]{style="color:#007F85;"}: recognizing that your emotions come from
  your own thoughts and unmet needs, and staying present enough under stress to notice a
  reaction without acting on it.
  - *Survey item:* "Knowing that my emotions stem from my own thoughts and unmet needs, my emotions are not caused by others."
- [**Authentic self-expression**]{style="color:#5A71A8;"}: stating your feelings, needs, and
  requests sincerely, without accusation, and staying open to any response.
  - *Survey item:* "Being responsible for my own experience, and willing to express my feelings and needs sincerely without accusation or criticism."
- [**Empathic listening**]{style="color:#C0522A;"}: staying open and flexible, and using
  conflict to connect rather than to win.
  - *Survey item:* "Listen patiently, try to understand other people from their perspective."

**Polarity:** Violent ↔ Nonviolent.

**Measure:** Nonviolent Communication Behaviors Scale (Cheung et al., 2022). Seven items
rated 1 = Never to 4 = Frequently.

## Find Your Score {.unnumbered}

Find your password below.

```{r}
#| label: wk11-communicator-compute
#| include: false
w11 <- dat |> transmute(Password = PASSWORD,
  `Self-connection`           = rowMeans(cbind(W11_1, W11_4)),
  `Authentic self-expression` = rowMeans(cbind(W11_2, W11_3)),
  `Empathic listening`        = rowMeans(across(W11_5:W11_7)))
```

```{r}
#| label: wk11-communicator-table
#| echo: false
score_table(w11$Password, list(`Self-connection`=w11$`Self-connection`,
  `Authentic self-expression`=w11$`Authentic self-expression`,
  `Empathic listening`=w11$`Empathic listening`),
  "11. Communicator: your NVCBS composites (1–4)")
```

## Locate Your Score {.unnumbered}

Scores for all peer mentors are visualized below. Locate your score relative to your peers.

```{r}
#| label: wk11-communicator-plot
#| echo: false
#| fig-width: 9
#| fig-height: 3.8
norm_facets(list(`Self-connection`=w11$`Self-connection`,
  `Authentic self-expression`=w11$`Authentic self-expression`,
  `Empathic listening`=w11$`Empathic listening`), xlab="Frequency",
  scale = c(1, 4), labels = c("1\nNever","2\nRarely","3\nSometimes","4\nFrequently"))
```

## Reflect and Plan

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** To be the best mentor you can be, what is one new thing you will try to do this week for mentees and/or your team?
:::

::: {.callout-tip}
## UGPM Meeting
Role play practice.
:::
