# 12. People Orientation {.unnumbered}

```{r}
#| include: false
source("_setup.R")
```

**Big Question:** *What is your view of people?*

**Constructs:** An implicit theory is your working assumption about whether people can
change. It matters for mentoring because it shapes how you read a struggling mentee.

- **Growth orientation**: people's basic characteristics can substantially change.
  - *Survey item:* "Everyone, no matter who they are, can significantly change their basic characteristics."
- **Fixed orientation**: the important parts of who someone is cannot really be changed.
  - *Survey item:* "The kind of person someone is, is something very basic about them and it can't be changed very much."

**Polarity:** Fixed ↔ Growth.

**Measure:** 'Kind of Person' Implicit Theory Scale (Dweck, 1999). Eight items rated 1–6.
Fixed-mindset items are reverse-scored, so a higher composite means a stronger **growth
mindset**.

## Your Scores {.unnumbered}

Find your password below.

```{r}
#| label: wk12-people-orientation-compute
#| include: false
w12 <- dat |> transmute(Password = PASSWORD,
  `Growth mindset` = rowMeans(cbind(7-W12_1, 7-W12_2, W12_3, 7-W12_4,
                                    W12_5, 7-W12_6, W12_7, W12_8)))
```

```{r}
#| label: wk12-people-orientation-table
#| echo: false
score_table(w12$Password, list(`Growth mindset`=w12$`Growth mindset`),
  "12. People Orientation: your growth mindset composite (1–6)")
```

## Class Distribution {.unnumbered}

```{r}
#| label: wk12-people-orientation-plot
#| echo: false
#| fig-width: 6
#| fig-height: 3.8
norm_facets(list(`Growth mindset`=w12$`Growth mindset`), xlab="Growth mindset (1–6)",
  scale = c(1, 6))
```

## Reflect

::: {.callout-warning}
## Journal
- **Score:** How does reflecting on your score help you think about who you are as a mentor?
- **Behavior:** What is one thing you will commit to this week that reflects this mindset?
:::
